### 2016-07-09 NLO.tex
set up of the calculation

\subsection{The Squark Production Cross Section at Next-to-Leading Order}
The squark production cross section at next-to-leading order is composed out of three contributions. These are the Born or tree-level cross section, the virtual correction and the real correction. 
\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}}\label{eq:BVR}
All three contributions have to be calculated with next-to-leading parton density functions.\\
It has been checked that for multiple different and quite distinct choices of the parameters $m_{\tilde{q}}$ and $m_{\tilde{g}}$, the double as well as the single poles of the virtual and real correction cancel up to machine precision. As the real corrections have been calculated analytically it is possible to quote the double pole. With
\sigma^{\mathrm{R}}_{\mathrm{double\ pole}} = -\sigma^{\mathrm{V}}_{\mathrm{double\ pole}} = C(F)\frac{\alpha_s}{\pi}\sigma^{\mathrm{B}} \frac{1}{\epsilon^2}
it has a very succinct form. \\
The setup of the calculation is summarized in fig. \ref{fig:CalcSetup}. Both the virtual and the Born matrix amplitude have been generated with the \texttt{Mathematica} package \texttt{FeynArts}. To this end a modelfile generated by the \texttt{Mathematica} package \texttt{SARAH} has been adjusted by hand to include counterterm Feynman rules and the definition of those counterterms. The matrix amplitudes have been processed further to the absolute squared matrix amplitudes by the \texttt{Mathematica} package \texttt{FormCalc} which have then been converted to \texttt{C++} and stored in an output file.\\
This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of the absolute squared matrix amplitudes numerically by using the package \texttt{LoopTools} \cite{Hahn:1998}. Finally the phase space integration and the integration over $x_1$ and $x_2$ is performed by the integration routine ``Cuhre'' which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}. The parton density functions are included using \texttt{LHAPDF6}\cite{Buckley:2014ana}\\
The computation of the real correction has been done by Wojciech Kotlarski, another member of the group. Comment on how real corrections are processed.\\

@@

	\node [block1a] at (-1,-3) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{B}|^2}$};	
	\node [block1a] at (-1,-1.5) (notebookV) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{1L}}$ \newline \texttt{FormCalc} $\to 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$};

@@

	\node [block5b] at (3.7,-3.5) (Born) {\underline{Born contribution} \newline \texttt{CUBA} $\to$ num. integration over $t, x_1, x_2$ to $\sigma^{\mathrm{B}}$};
	\node [block5b] at (7.5,-2.7) (Virt) {\underline{Virtual correction}\newline \texttt{LoopTools} $\to$ computation \newline of $ 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$ \newline \texttt{CUBA} $\to$ num. integration over $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$};
	\node [block5c] at (11.5,-3.3) (Real) {\underline{Real correction}\newline \texttt{MADGRAPH} $\to$ $\mathcal{M}^{\mathrm{R}}$, phase space slicing\newline \texttt{CUBA} $\to$ num. integration to $\sigma^{\mathrm{R}}$};
	\path [line, line width = 1] (1.2,-3) -- (1.9,-3);
	\path [line, line width = 1] (1.2,-1.5) -- (5.7,-1.5);
	\node [block6a] at (7.5,-6.5) (Sigma) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}}$};

@@

	\path [line, line width = 1] (Real) -- (Sigma);

@@

\caption{This scheme illustrates the setup of the computation of the next-to-leading order cross section. The absolute squared matrix amplitudes of the Born or tree-level contribution and the virtual correction are generated by \texttt{Mathematica} packages and imported into a \texttt{C++} code. Loop integrals are evaluated numerically using \texttt{Looptools}. For all three contributions the \texttt{CUBA}-library was used for the phase space and $x_1$ and $x_2$ integration to arrive at the cross sections $\sigma^{\mathrm{B}}$, $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{V}}$.  The real corrections have been calculated by Wojciech Kotlarski, another member of the group.}\label{fig:CalcSetup}

@@

>>>>

\subsection{The Squark Production Cross Section at Next-to-Leading Order}
The squark production cross section at next-to-leading order is composed out of three contributions. These are the Born (tree-level) cross section, the virtual correction and the real correction. 
\begin{align}
\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}}\label{eq:BVR}
\end{align}
All three contributions have to be calculated with next-to-leading order parton density functions. The next section summaries how the calculation has been performed.

\subsubsection{The Set Up of the calculation}
The setup of the calculation is summarized in fig. \ref{fig:CalcSetup}. Both the virtual and the Born matrix amplitude have been generated with the \texttt{Mathematica} package \texttt{FeynArts}. To this end a modelfile, generated by the \texttt{Mathematica} package \texttt{SARAH}, has been adjusted to include counterterm Feynman rules and appropriate renormalization constants. This procedure was explained in section \ref{sec:MatrixElRen}. The matrix amplitudes have been processed further to $\sum|\mathcal{M}^{\mathrm{B}}|^2$ and $ \sum 2\Re (\mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast})$ by the \texttt{Mathematica} package \texttt{FormCalc} before this output has then been converted to a \texttt{C++} readable code and stored in an output file.\\
This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of $ \sum 2\Re (\mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast})$ numerically by using the package \texttt{LoopTools}. Finally the phase space integration and the integration over $x_1$ and $x_2$ is performed by the integration routine ``Cuhre'' which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}. The parton density functions are included using \texttt{LHAPDF6}\cite{Buckley:2014ana}\\
The computation of the real corrections have been done by Wojciech Kotlarski, another member of the group. To extract the singularities from the real corrections, the ``two cut phase space slicing method'' outlined in section \ref{sec:RealGluonRad}, has been used. For the soft and hard collinear limit, the absolute squared matrix element has been calculated with \texttt{FormCalc} and analytically integrated over the gluons four-momentum in $D$ dimensions in \texttt{Mathematica}. This has been exported to the \texttt{C++} code to perform the rest of the integration numerically with the \texttt{CUBA} library. The matrix element in the hard non-collinear regime has been imported from \texttt{MadGraph5}\cite{Alwall:2014hca}and the whole integration has been performed numerically by the \texttt{CUBA} library.

@@

	\node [block1a] at (-1,-2.1) (notebookR) {soft/collinear limit: \newline \texttt{FeynArts} $\to \mathcal{M}^{\mathrm{R}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{R}|^2}$};
	\node [block1a] at (-1,-7) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{B}|^2}$};	
	\node [block1a] at (-1,-4.7) (notebookV) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{1L}}$ \newline \texttt{FormCalc} $\to$ \newline $2\sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$};

@@

	\node [block5b] at (3.7,-7.3) (Born) {\underline{Born contribution} \newline \texttt{CUBA} $\to$ \newline integration over \newline $t, x_1, x_2$ to $\sigma^{\mathrm{B}}$};
	\node [block5b] at (7.5,-6.5) (Virt) {\underline{Virtual correction}\newline \texttt{LoopTools} $\to$ \newline computation of $ 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$ \newline \texttt{CUBA} $\to$ \newline integration over \newline $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$ };
	\node [block5c] at (11.5,-4.6) (Real) {\underline{Real correction}\newline phase space slicing: \newline $\bullet$ soft/collinear part \newline from \texttt{Mathematica},\newline \texttt{CUBA} three dimen- \newline sional integration to $\sigma^{\mathrm{R}}_{\mathrm{S}}$ and $\sigma^{\mathrm{R}}_{\mathrm{HC}}$ \newline $\bullet$ hard non-collinear \newline part from \newline \texttt{MADGRAPH}, \newline  \texttt{CUBA} $\to$ seven \newline dimensional \newline integration to $\sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$ \newline $\sigma^{\mathrm{R}} = \sigma^{\mathrm{R}}_{\mathrm{S}} + \sigma^{\mathrm{R}}_{\mathrm{HC}} + \sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$};
	\path [line, line width = 1] (1.2,-7.0) -- (1.9,-7.0);
	\path [line, line width = 1] (1.2,-4.9) -- (5.7,-4.9);
	\path [line, line width = 1] (1.2,-2.0) -- (9.5,-2.0);
	\node [block6a] at (7.5,-10) (Sigma) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}} + \sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$};

@@

	\path [line, line width = 1] (10,-8.45) -- (Sigma);

@@

\caption{This scheme illustrates the setup of the computation of the next-to-leading order cross section. The (absolute) squared matrix amplitudes of the Born contribution the virtual correction and the real correction in the soft and/or collinear limit are generated by \texttt{Mathematica} packages and imported into a \texttt{C++} code. The amplitude from the real corrections is analytically integrated over the gluon's four momentum in $D$ dimensions. Loop integrals are evaluated numerically using \texttt{Looptools}. For the hard non-collinear regime, the matrix amplitude of the real corrections is imported from \texttt{MadGraph5}. The \texttt{CUBA}-library was used for all three contributions to perform the remaining integration to arrive at the cross sections $\sigma^{\mathrm{B}}$, $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{R}}$.}\label{fig:CalcSetup}

@@

\end{figure}\\
It has been checked that for multiple different and quite distinct choices of the parameters $m_{\tilde{q}}$ and $m_{\tilde{g}}$, the double as well as the single poles of the virtual and real correction cancel up to machine precision. As the poles of the real corrections have been calculated analytically, it is possible to quote them. The double pole is actually proportional to the Born cross section:
\sigma^{\mathrm{R}}_{\mathrm{double\ pole}} = -\sigma^{\mathrm{V}}_{\mathrm{double\ pole}} = C(F)\frac{\alpha_s}{\pi}\sigma^{\mathrm{B}} \frac{1}{\epsilon^2}.

### 2016-07-09 Renormalization.tex
set up of the calculation

\subsection{The Beta Function}\label{sec:beta_function}
The beta function describes the dependence of the gauge coupling $g_s$ upon the energy scale $\mu$.\\
Writing down the action of a theory in $D$ dimensions, one needs to introduce an energy scale $\mu$ in order to keep the action dimensionless. But $\mu$ is no physical parameter but can be absorped into the fields and parameters. To this end one defines
\begin{align}
g_{sB}(g_s, \mu) = \mu^\epsilon g_s \left( 1 + \frac{\delta g_s}{g_s} \right)
\end{align}
which must not depend upon the unphysical scale $\mu$, ergo
\begin{align}
0 = \frac{\mathrm{d}g_{sB}}{\mathrm{d}\ln\mu} = \frac{\partial g_{sB}}{\partial \ln\mu} + \beta \frac{\partial g_{sB}}{\partial g_s}\label{eq:beta_func}
\end{align}
where the definition of the beta function $\frac{\partial g_s}{\partial\ln\mu}$ has been inserted. Equation \eqref{eq:beta_func} serves to calculate $\beta(g_s,\epsilon)$.  By equating coefficients and using the shortcuts
\begin{align*}
\frac{\beta_0^L}{2} &= \frac{2}{3}T(F)(n_f-1) - \frac{11}{6}C(A)\\
\frac{\beta_0^H}{2} &= \frac{5}{6}C(A) + \frac{2}{3}T(F) + \frac{1}{3}T(F)n_f\\
L &= - \frac{2}{3} C(A) \ln \frac{m_{\tilde{g}}^2}{\mu^2} - \frac{1}{3}T(F)n_f \ln \frac{m_{\tilde{q}}^2}{\mu^2} - \frac{2}{3}T(F) \ln \frac{m_t^2}{\mu^2}-\frac{1}{12} C(A) \left( \ln \frac{m_{\phi^0}^2}{\mu^2} + \ln \frac{m_{\sigma^0}^2}{\mu^2} \right)
\end{align*}
so that 
\begin{align}
\frac{\delta g_s}{g_s} = \frac{g_s^2}{16\pi^2}\left( \frac{\beta^L_0}{2\epsilon_{\mathrm{UV}}} + \frac{\beta^H_0}{2\epsilon_{\mathrm{UV}}} + L \right)
\end{align}
one finds
\begin{align}
\beta(g_s,\epsilon) &= -\epsilon g_s \left( 1 + \frac{g_s^2}{16\pi^2} L \right) + \beta(g_s) + \mathcal{O}(\mathrm{2-loop})\\
\beta(g_s) &= \frac{g_s^3}{16\pi^2} \beta_0^L + \mathcal{O}(\mathrm{2-loop}).
\end{align}
This is the beta function of QCD first found by Politzer \cite{Politzer:1973fx} Gross and Wilczek \cite{Gross:1973ju}. This means that renormalizing $g_s$ in the way it is, decouples heavy particles from the $\beta$ function and allows to adopt $\alpha_s = \frac{g_s^2}{4\pi}$ from the parton density functions.

@@

\subsection{The Renormalization of the Matrix Element}
This section explains how the renormalization of the RSQCD is implemented in the framework of the automated calculation and gives intermediate results in the form of the renormalized matrix element.

@@

+ B0i[bb1, Pair[k[1], k[1]], 0, 0]) - 1/6 B0i[bb1, Pair[k[1], k[1]], MassGlu^2, MassSu[1]^2]) Mat[([<u2|6 k[1]|u1>]) SUNT[Col1, Col2]] 

@@

+ B0i[bb1, Pair[k[1], k[1]], 0, 0]) - 1/6 B0i[bb1, Pair[k[1], k[1]], MassGlu^2, MassSu[4]^2]) Mat[(<u2|7 k[1]|u1>]) SUNT[Col1, Col2]]]

@@

To extract infrared divergences, \texttt{LoopTools} has been used. This package provides the function \texttt{SetLambda} which can be set to 0, $-1$ or $-2$ to extract the finite part, $\frac{1}{\epsilon}$ pole or $\frac{1}{\epsilon^2}$ pole of scalar integrals in dimensioanl regularisation. \texttt{SetLambda} includes both, UV and IR poles. In fact, the function \texttt{SetUVDiv} controls whether UV divergences are kept (\texttt{SetUVDiv}$\to 1$) or discarded (\texttt{SetUVDiv}$\to 0$), which presents another check of UV-finiteness which has been performed.\\

@@

The upper plot in figure \ref{fig:MatrixElement} shows the finite contributions from loop diagrams with different topology to $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$ as a function of the Mandelstam variable $t$ where $\frac{1}{4\cdot 9}$ is the averaging over final state spins and colors. The lower plot displays the tree-level absolute squared matrix amplitude with leading order $\alpha_s$ which is compared to its analogue with next-to-leading order $\alpha_s$ and virtual correction $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$. The latter is not given analytically. All terms are color and spin averaged in the final state and summed over in the initial state.

>>>>

\subsection{The Beta Function}\label{sec:beta_function}
The beta function describes the dependence of the gauge coupling $g_s$ upon the energy scale $\mu$.\\
Writing down the action of a theory in $D$ dimensions, one needs to introduce an energy scale $\mu$ in order to keep the action dimensionless. But $\mu$ is no physical parameter but can be absorped into the fields and parameters. To this end one defines
\begin{align}
g_{sB}(g_s, \mu) = \mu^\epsilon g_s \left( 1 + \frac{\delta g_s}{g_s} \right)
\end{align}
which must not depend upon the unphysical scale $\mu$, ergo
\begin{align}
0 = \frac{\mathrm{d}g_{sB}}{\mathrm{d}\ln\mu} = \frac{\partial g_{sB}}{\partial \ln\mu} + \beta \frac{\partial g_{sB}}{\partial g_s}\label{eq:beta_func}
\end{align}
where the definition of the beta function $\frac{\partial g_s}{\partial\ln\mu}$ has been inserted. Equation \eqref{eq:beta_func} serves to calculate $\beta(g_s,\epsilon)$.  By equating coefficients and using the shortcuts
\begin{align*}
\frac{\beta_0^L}{2} &= \frac{2}{3}T(F)(n_f-1) - \frac{11}{6}C(A)\\
\frac{\beta_0^H}{2} &= \frac{5}{6}C(A) + \frac{2}{3}T(F) + \frac{1}{3}T(F)n_f\\
L &= - \frac{2}{3} C(A) \ln \frac{m_{\tilde{g}}^2}{\mu^2} - \frac{1}{3}T(F)n_f \ln \frac{m_{\tilde{q}}^2}{\mu^2} - \frac{2}{3}T(F) \ln \frac{m_t^2}{\mu^2}-\frac{1}{12} C(A) \left( \ln \frac{m_{\phi^0}^2}{\mu^2} + \ln \frac{m_{\sigma^0}^2}{\mu^2} \right)
\end{align*}
so that 
\begin{align}
\frac{\delta g_s}{g_s} = \frac{g_s^2}{16\pi^2}\left( \frac{\beta^L_0}{2\epsilon_{\mathrm{UV}}} + \frac{\beta^H_0}{2\epsilon_{\mathrm{UV}}} + L \right)
\end{align}
one finds
\begin{align}
\beta(g_s,\epsilon) &= -\epsilon g_s \left( 1 + \frac{g_s^2}{16\pi^2} L \right) + \beta(g_s) + \mathcal{O}(\mbox{2-loop})\\
\beta(g_s) &= \frac{g_s^3}{16\pi^2} \beta_0^L + \mathcal{O}(\mbox{2-loop}).
\end{align}
This is the beta function of QCD first found by Politzer \cite{Politzer:1973fx}, Gross and Wilczek \cite{Gross:1973ju}. This means that renormalizing $g_s$ in the way it is, decouples heavy particles from the $\beta$ function and allows to adopt $\alpha_s = \frac{g_s^2}{4\pi}$ from the parton density functions.

@@

\subsection{The Renormalization of the Matrix Element}\label{sec:MatrixElRen}
This section explains how the renormalization of the RSQCD is implemented in the framework of the automated calculation and gives intermediate results in the form of the renormalized matrix element.

@@

+ B0i[bb1, Pair[k[1], k[1]], 0, 0]) 
- 1/6 B0i[bb1, Pair[k[1], k[1]], MassGlu^2, MassSu[1]^2]) 
Mat[([<u2|6 k[1]|u1>]) SUNT[Col1, Col2]] 

@@

+ B0i[bb1, Pair[k[1], k[1]], 0, 0]) 
- 1/6 B0i[bb1, Pair[k[1], k[1]], MassGlu^2, MassSu[4]^2]) 
Mat[(<u2|7 k[1]|u1>]) SUNT[Col1, Col2]]]

@@

To extract infrared divergences, \texttt{LoopTools}\cite{Hahn:1998} has been used. This package provides the function \texttt{SetLambda} which can be set to 0, $-1$ or $-2$ to extract the finite part, $\frac{1}{\epsilon}$ pole or $\frac{1}{\epsilon^2}$ pole of scalar integrals in dimensioanl regularisation. \texttt{SetLambda} includes both, UV and IR poles. In fact, the function \texttt{SetUVDiv} controls whether UV divergences are kept (\texttt{SetUVDiv}$\to 1$) or discarded (\texttt{SetUVDiv}$\to 0$), which presents another check of UV-finiteness which has been performed.\\

@@

The upper plot in figure \ref{fig:MatrixElement} shows the finite contributions from loop diagrams with different topology to $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$ as well as their sum as a function of the Mandelstam variable $t$ where $\frac{1}{4\cdot 9}$ is the averaging over final state spins and colors. The lower plot displays the tree-level absolute squared matrix amplitude with leading order $\alpha_s$ which is compared to its analogue with next-to-leading order $\alpha_s$ and virtual correction $\frac{1}{4\cdot 9}\sum 2 \Re (\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}})$. The latter is not given analytically. All terms are color and spin averaged in the final state and summed over in the initial state.

### 2016-07-09 Virt_Real.tex
set up of the calculation

\subsubsection*{Real Gluon Radiation}
A representative set of Feynman-diagrams for real gluon emission are shown in fig. \ref{fig:RealGluon}. In order to extract the singularities the so called ``two-cut phase space slicing method''\cite{Harris:2001sx} has been adopted. Within this approach, the phase space has been divided into different regimes: a soft part ($S$), a hard collinear part ($HC$) and a hard non-collinear part ($H\overline{C}$):
\begin{align}
\sigma^{\mathrm{R}} = \int_S \mathrm{d}\sigma^{\mathrm{R}} + \int_H \mathrm{d}\sigma^{\mathrm{R}} = \int_S \mathrm{d}\sigma^{\mathrm{R}} + \int_{HC} \mathrm{d}\sigma^{\mathrm{R}} + \int_{H\overline{C}}\mathrm{d} \sigma^{\mathrm{R}}.
\end{align}
In the soft part, the energy of the outgoing gluon is only integrated up to  $\delta_s \frac{\sqrt{s}}{2}$ where $\delta_s$ is a cut on which the final result must not depend on and $\sqrt{s}$ is the center of mass energy of the colliding partons. A second cut $\delta_c$ is introduced to separate the collinear from the non-collinear region. After dividing the phase space into the three mentioned parts, each integration is performed separately. In the parts containing divergences, i.e. the soft and hard collinear part, the integration over the gluons four-momentum is performed analytically in $D = 4 - 2\epsilon$ dimensions. After performing mass factorization and adding up all three contributions, the real corrections do not depend on the two cut parameters $\delta_s$ and $\delta_c$. Furthermore the $\frac{1}{\epsilon^2}$ and $\frac{1}{\epsilon}$ poles have exactly the opposite sign of the ones extracted from the virtual corrections.

\subsubsection*{Real Quark Radiation}
As already mentioned before, adding up virtual and real gluon emission contributions results in the cancellation of divergences. However, there is a further contribution to squark production at next-to-leading order. This involves the radiation of an additional antiquark in the final state. To meet color conservation, the initial state has to be composed of a quark and a gluon, see fig. \ref{fig:quarkradiation}.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
\begin{scope}[shift={(0,0.25)}]
	\draw[fermion] (-1.25,0.75)--(-0.5,0);
	\draw[gluon] (-1.25,-0.75)--(-0.5,0);
	\draw[fermion] (-0.5,0)--(0.5,0); 
	\draw[scalar] (0.5,0)--(1.25,0.75);
	\draw[gluon] (0.5,0)--(1.25,-0.75);
	\draw[fermionnoarrow] (0.5,0)--(1.25,-0.75);
	\draw[scalar] (1.25,-0.75)--(2,0);
	\draw[fermion] (2,-1.5)--(1.25,-0.75);
	\end{scope}
\begin{scope}[shift={(3,0)}]
	\draw[fermion] (0,1)--(1,1);	
	\draw[gluon] (0,-0.5)--(1,-0.5);
	\draw[fermionnoarrow] (1,1)--(1,-0.5);
	\draw[gluon] (1,1)--(1,-0.5);
	\draw[scalar] (1,1)--(2.75,1);
	\draw[fermionnoarrow] (1,-0.5)--(2,-0.5);
	\draw[gluon] (1,-0.5)--(2,-0.5);
	\draw[scalar] (2,-0.5)--(2.75,0.25);
	\draw[fermion] (2.75,-1.25)--(2,-0.5);
\end{scope}
\begin{scope}[shift={(7,0)}]
	\draw[fermion] (0,1)--(1,1);
	\draw[gluon] (0,-1)--(1,-1);
	\draw[fermionnoarrow] (1,1)--(1,0);
	\draw[gluon] (1,1)--(1,0);
	\draw[fermion] (1,-1)--(1,0);
	\draw[scalar] (1,1)--(2,1);
	\draw[fermion] (2,-1)--(1,-1);
	\draw[scalar] (1,0)--(2,0);
\end{scope}
\end{tikzpicture}
\caption{A selection of real quark emission diagrams contributing to squark production. The first two diagrams have a gluino propagator which may go on-shell. In this regime of phase space these diagrams should not be included in the correction to squark-production but to a tree-level contribution to squark-gluino-production.}\label{fig:quarkradiation}
\end{center}
\end{figure}
These contributions do not comprise soft divergences. A split-up of space space in a soft and a hard part is therefore not needed. However, there are collinear singularities, originating from initial state radiation like shown in the last diagram of \ref{fig:quarkradiation}, which again have to be removed by means of mass factorization.\\
But there is another complication: The first and second diagram in fig. \ref{fig:quarkradiation} include a gluino which subsequently decays into a squark-antiquark pair. If the squared gluino's four-momentum approaches its mass-shell $p^2 = m^2_{\tilde{g}}$ the amplitude of this diagram hits a singularity. Of course, this can only happen if $m_{\tilde{g}} > m_{\tilde{q}}$.\\
These singularities are treated by introducing a non-zero width $\Gamma_{\tilde{q}}$ for the gluino as a regulator, i.e. modifying the propagator to the Breit-Wigner form
\begin{align}
\frac{1}{p^2 - m_{\tilde{q}}^2} \to \frac{1}{p^2 - m_{\tilde{q}}^2 + i m_{\tilde{q}} \Gamma_{\tilde{q}}}.
\end{align}
Integrating over the regime of phase space, where the gluino approaches its mass-shell, actually gives the tree-level contribution of the process $qG \to \tilde{q}\tilde{g}$ weighted by the branching ratio $\frac{\Gamma_{\tilde{q}\to q \tilde{g}}}{\Gamma_{\tilde{q}}}$. To avoid double counting, one has to cut this very regime of phase space out and subtract it from the total contribution originating from those diagrams. For a detailed prescription on how to deal with this issue, see \cite{Beenakker:1996ch, Gavin:2013kga}.

>>>>

\subsubsection{Real Gluon Radiation}\label{sec:RealGluonRad}
A representative set of Feynman-diagrams for real gluon emission are shown in fig. \ref{fig:RealGluon}. In order to extract the singularities the so called ``two cut phase space slicing method''\cite{Harris:2001sx} has been adopted. Within this approach, the phase space has been divided into different regimes: a soft part ($S$), a hard collinear part ($HC$) and a hard non-collinear part ($H\overline{C}$):
\begin{align}
\sigma^{\mathrm{R}} = \int_S \mathrm{d}\sigma^{\mathrm{R}} + \int_H \mathrm{d}\sigma^{\mathrm{R}} = \int_S \mathrm{d}\sigma^{\mathrm{R}} + \int_{HC} \mathrm{d}\sigma^{\mathrm{R}} + \int_{H\overline{C}}\mathrm{d} \sigma^{\mathrm{R}}.
\end{align}
In the soft part, the energy of the outgoing gluon is only integrated up to  $\delta_s \frac{\sqrt{s}}{2}$ where $\delta_s$ is a cut on which the final result must not depend on and $\sqrt{s}$ is the center of mass energy of the colliding partons. A second cut $\delta_c$ is introduced to separate the collinear from the non-collinear region. After dividing the phase space into the three mentioned parts, each integration is performed separately. In the parts containing divergences, i.e. the soft and hard collinear part, the integration over the gluons four-momentum is performed analytically in $D = 4 - 2\epsilon$ dimensions. After performing mass factorization and adding up all three contributions, the real corrections do not depend on the two cut parameters $\delta_s$ and $\delta_c$. Furthermore the $\frac{1}{\epsilon^2}$ and $\frac{1}{\epsilon}$ poles have exactly the opposite sign of the ones extracted from the virtual corrections.

\subsubsection{Real Quark Radiation}
As already mentioned before, adding up virtual and real gluon emission contributions results in the cancellation of divergences. However, there is a further contribution to squark production at next-to-leading order. This involves the radiation of an additional antiquark in the final state. To meet color conservation, the initial state has to be composed of a quark and a gluon, see fig. \ref{fig:quarkradiation}.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
\begin{scope}[shift={(0,0.25)}]
	\draw[fermion] (-1.25,0.75)--(-0.5,0);
	\draw[gluon] (-1.25,-0.75)--(-0.5,0);
	\draw[fermion] (-0.5,0)--(0.5,0); 
	\draw[scalar] (0.5,0)--(1.25,0.75);
	\draw[gluon] (0.5,0)--(1.25,-0.75);
	\draw[fermionnoarrow] (0.5,0)--(1.25,-0.75);
	\draw[scalar] (1.25,-0.75)--(2,0);
	\draw[fermion] (2,-1.5)--(1.25,-0.75);
	\end{scope}
\begin{scope}[shift={(3,0)}]
	\draw[fermion] (0,1)--(1,1);	
	\draw[gluon] (0,-0.5)--(1,-0.5);
	\draw[fermionnoarrow] (1,1)--(1,-0.5);
	\draw[gluon] (1,1)--(1,-0.5);
	\draw[scalar] (1,1)--(2.75,1);
	\draw[fermionnoarrow] (1,-0.5)--(2,-0.5);
	\draw[gluon] (1,-0.5)--(2,-0.5);
	\draw[scalar] (2,-0.5)--(2.75,0.25);
	\draw[fermion] (2.75,-1.25)--(2,-0.5);
\end{scope}
\begin{scope}[shift={(7,0)}]
	\draw[fermion] (0,1)--(1,1);
	\draw[gluon] (0,-1)--(1,-1);
	\draw[fermionnoarrow] (1,1)--(1,0);
	\draw[gluon] (1,1)--(1,0);
	\draw[fermion] (1,-1)--(1,0);
	\draw[scalar] (1,1)--(2,1);
	\draw[fermion] (2,-1)--(1,-1);
	\draw[scalar] (1,0)--(2,0);
\end{scope}
\end{tikzpicture}
\caption{A selection of real quark emission diagrams contributing to squark production. The first two diagrams have a gluino propagator which may go on-shell. In this regime of phase space these diagrams should not be included in the correction to squark-production but to a tree-level contribution to squark-gluino-production.}\label{fig:quarkradiation}
\end{center}
\end{figure}
These contributions do not comprise soft divergences. A split-up of space space in a soft and a hard part is therefore not needed. However, there are collinear singularities, originating from initial state radiation like shown in the last diagram of \ref{fig:quarkradiation}, which again have to be removed by means of mass factorization.\\
But there is another complication: The first and second diagram in fig. \ref{fig:quarkradiation} include a gluino which subsequently decays into a squark-antiquark pair. If the squared gluino's four-momentum approaches its mass-shell $p^2 = m^2_{\tilde{g}}$ the amplitude of this diagram hits a singularity. Of course, this can only happen if $m_{\tilde{g}} > m_{\tilde{q}}$.\\
These singularities are treated by introducing a non-zero width $\Gamma_{\tilde{q}}$ for the gluino as a regulator, i.e. modifying the propagator to the Breit-Wigner form
\begin{align}
\frac{1}{p^2 - m_{\tilde{q}}^2} \to \frac{1}{p^2 - m_{\tilde{q}}^2 + i m_{\tilde{q}} \Gamma_{\tilde{q}}}.
\end{align}
Integrating over the regime of phase space, where the gluino approaches its mass-shell, actually gives the tree-level contribution of the process $qG \to \tilde{q}\tilde{g}$ weighted by the branching ratio $\frac{\Gamma_{\tilde{q}\to q \tilde{g}}}{\Gamma_{\tilde{q}}}$. To avoid double counting, one has to cut this very regime of phase space out and subtract it from the total contribution originating from those diagrams. For a detailed prescription on how to deal with this issue, see \cite{Beenakker:1996ch, Gavin:2013kga}.
